Industrial, large-scale model predictive control with structured neural networks

### 2020-10-21 paper.tex
minor change.

\begin{abstract}
The design of neural networks (NNs) is presented 
for treating large, linear model predictive control (MPC) applications that 
are out of reach with available quadratic programming (QP)
solvers. First, we introduce a new feedforward
network architecture that enables practitioners to 
obtain offset-free closed-loop performance with NNs.
Second, we discuss the data generation procedure 
to sample the relevant state space for the network 
training based on anticipated online setpoint changes and
plant disturbances. Third, we use the 
input-to-state stability results 
available in the MPC literature
and establish robustness 
properties of NN controllers.
Finally, we present illustrative
simulation studies on 
process control examples. 
We apply the NN design approach
and compare the performance with online QP based MPC on an industrial crude
distillation unit model with 252 states, 32 control inputs, 
and a control-sample horizon length of 140. Parallel computing 
is used for data generation and graphical processing units are used for
network training. All the anticipated plant operational scenarios 
with setpoints and disturbances that may change for 
a reasonable duration of operation must be sampled for NN training.
After the offline design phase, 
NNs execute MPC 
three to five orders of magnitude faster
than an available QP solver with less than $1\%$
loss in the closed-loop performance.
\end{abstract}

>>>>

\begin{abstract}
The design of neural networks (NNs) is presented 
for treating large, linear model predictive control (MPC) applications that 
are out of reach with available quadratic programming (QP)
solvers. First, we introduce a new feedforward
network architecture that enables practitioners to 
obtain offset-free closed-loop performance with NNs.
Second, we discuss the data generation procedure 
to sample the relevant state space for the network 
training based on anticipated online setpoint changes and
plant disturbances. Third, we use the 
input-to-state stability results 
available in the MPC literature
and establish robustness 
properties of NN controllers.
Finally, we present illustrative
simulation studies on 
process control examples. 
We apply the NN design approach
and compare the performance with online QP based MPC on an industrial crude
distillation unit model with 252 states, 32 control inputs, 
and a control-sample horizon length of 140. Parallel computing 
is used for data generation and graphical processing units are used for
network training. All the anticipated plant operational scenarios 
with setpoints and disturbances that may change
during operation must be sampled for NN training.
After the offline design phase, 
NNs execute MPC 
three to five orders of magnitude faster
than an available QP solver with less than $1\%$
loss in the closed-loop performance.
\end{abstract}
